\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2018-02-20 redaction/dhp_july2017.tex
changement texte début

\begin{abstract}
This paper investigates the underlying sources behind the downward trend of international transport costs, exploiting information contained in the US imports flows database over 1974-2013 distinguished by transport mode, air and vessel, in line with \cite{hummels2007}. This drives us to provide a careful modeling of international transport costs, that allows for both ad-valorem (multiplicative) and per-unit (additive) components. In contrast to \cite{hummels2007}, we find that composition effects play a minor role in accounting for the reduction of transport costs relative to the value of US imports. Transport cost ``per se'' did decline. Importantly, this difference of results can be attributed to the new way of modeling the additive component of transport costs we offer. Further, in quantitative terms, we find that the additive component of transport costs is sizeable, representing between 40 and 50\% of overall transport costs. In both aspects, our results point the importance of the additive component in accounting for international transport costs.
\end{abstract}

@@

This focus is shared with part of the international trade literature that studies the patterns of transport costs over time, such as \cite{hummels2007} and \cite{Behar_Venables} (among others). Many argue that transport costs have substantially decreased with technological advance in transportation, infrastructure development and new communication technologies (see \citealp{Lafourcade_Thisse}). %According to \cite{Glaeser04}, over the twentieth century, the cost of moving goods inland have declined by over 90\% in real terms.
The container was a major transport-cost reducing innovation (see \citealp{levinson2016box}). However, \cite{hummels2007} points out that trade composition effects dominate the characterization of time trends of international transport costs and that transport costs ``per se'' (i.e., \textit{ceteris paribus} for given goods, mode, and trade routes) have not declined much. In this paper, we investigate the robustness of this result. As a major contribution of the paper, and in contrast to \cite{hummels2007}, we find that trade composition effects play a minor role in accounting for the trend patterns of transport costs. Rather, transport costs ``per se'' did decline, in both transport modes, and this is constitutes the main driving force behind the overall transport costs decrease, in particular for air transport.\medskip

To prove this point we provide a careful modelling of transport costs. Following \citet{samuelson1954}, standard models of international trade have usually modeled trade costs as an \emph{ad-valorem} tax equivalent (ie, as a constant percentage of the producer price per unit traded, part of the ``iceberg cost'' hypothesis).\footnote{Strictly speaking, the ``iceberg cost'' includes both the ad-valorem dimension of trade cost and the fact that these costs are paid in terms of the good that is traded. As this last element is irrelevant in our case, we use the terms ``iceberg'' and ``ad-valorem'' interchangeably, as it is commonly done in the literature.} However, a recent strand of the literature points out to the existence of an additive component, that is, a cost per unit traded.\footnote{As documented by \cite{Irrazabal_2015}, pricing structure in shipping, additive tariffs, distribution costs... often exhibit (at least partly) an additive structure.} Based on US sectoral data, our own estimates also bring out the importance of additive costs in international transport costs. This is obtained by providing an empirical decomposition of the structure of transport costs over time, in which we explicitly distinguish between ad-valorem and additive parts. To do so, we exploit information contained in the US imports flows over 1974-2013, from which we get a measure of international transport costs as the difference between the import and the export prices, on a year-product-partner country basis. This database is the same as \cite{hummels2007}, extended over the more recent years (2005-2013). \smallskip

Our results may be summarized in two main new findings. First, additive transport costs are quantitatively sizeable. On average over 1974-2013, the additive cost is estimated to be 1.8\% and 2.9\% of the export price in air and vessel transport respectively. This is slightly lower than our estimates for the ad-valorem component (3.5\% and 3.2\% for air/vessel respectively on average over the period). Put it differently, additive costs represent between 40 \% and 50\% of the overall transport costs, depending on the year and the transport mode. To the best of our knowledge, our paper is the first to provide such an extensive quantitative measure of both ad-valorem and additive costs in total transport costs.\footnote{As we discuss below, the closest paper to us in this respect is \citet{Irrazabal_2015}. However, given their database and their empirical approach, \citet{Irrazabal_2015} can only identify the ratio of the additive to the ad-valorem cost ($\frac{t_{ik}}{\tau_{ik}}$ in our terminology), that they interpret by expressing it in terms of the median export price by country-product ($\bar{\widetilde{p}}_{ik}$). By contrast, our estimation strategy enables us to uncover both values of the ad-valorem and the additive costs $\tau_{ik}$ and $t_{ik}$ separately, in terms of the country-product export price $\widetilde{p}_{ik}$.} This represents a valuable insight for calibrating related international trade or business cycle models. We also provide an empirical assessment of what standard international trade models lose by skipping additive transport costs. Quantitatively, the omission of the additive term leads to overestimate the ad-valorem component by roughly a factor~2. Additionnaly, the goodness of fit is systematically better when the additive component is included in the regression, even when taking into account the additional degrees of freedom.

Second, we find that the main source of the downward trend in overall transport costs over 1974-2013 does come from the reduction of transport cost ``per se'', rather than from trade composition effects.\footnote{Between 1974 and 2013, transport costs as a share of export prices have decreased by roughly 50\% in air shipping and 60\% in vessel shipping.} This stands in sharp contrast to the conclusion obtained by \cite{hummels2007} on the same database (until 2004). Importantly, we show that the difference of results can be attributed to the new way of modeling of the additive component we offer. Allowing the additive costs to vary  across products and country partners (rather than being constant as in \cite{hummels2007}), turns out to be key in the decomposition of underlying sources of the decrease of overall transport costs observed over the period. Our result is more in line with common knowledge observations of the reduction of transport costs due, e.g., to the diffusion of the container.\smallskip

In both aspects, our results point the importance of the additive component in accounting for international transport costs. In this respect, it contributes to the literature that challenges the dominant role of iceberg costs in international trade (even in the case of ice transport: see \citealp{bosker2018ice}). As pointed out by \cite{alchian}, the relative price of two varieties of some good will depend on the level of trade costs as long as they display an additive component. In this context, the relative demand for more expensive/higher quality product goods increases with trade costs (``shipping the good apples out''). This is consistent with the findings by \citet{hummels_skiba}, who estimate the elasticity of freight rates with respect to price to be well below unity. Also, their estimates imply that doubling freight costs increases average free alongside (fas) export prices by 80 to 141 percent, consistent with high quality goods being sold in markets with high freight costs. \citet{Lashkaripour-mimeo-2017} challenges this view. Highlighting that more expensive goods are systematically heavier (and hence more costly to transport\footnote{Yet, one can be concerned by the generality of this result. While the positive correlation between weight and price seems reasonable for goods from the second industrial revolution like cars, it is dubious in the case of ITC goods whose importance in international trade has been rising since the end of the twentieth century.}), he finds an average transport cost elasticity much closer to 1 using firm-level data on Colombian imports. This result is also confirmed on more aggregate US, sector-level trade data. The debate is not over yet, as recent empirical studies based on micro-level data conversely provide a strong empirical support to the role of additive costs (i.e., cost per unit exported) in international trade costs. Based on a firm-product-level database of French exporters, \citet{martin2012} finds that firms charge higher unit values for exports to more remote countries, in contradiction with the ad-valorem hypothesis.\footnote{Beyond the positive aspect, several recent papers also point out the normative implications of additive trade costs. \citet{sorensen2014} extends \citet{melitz}'s seminal model of international trade by including additive trade costs, in addition to the ad-valorem component. A key analytical result is that the welfare gain from a reduction in trade barriers is higher for a decrease in additive costs than a decrease in ad-valorem costs, due to the alteration of relative prices in a heterogeneous-firms trade framework. This is confirmed by \cite{Irrazabal_2015}. While these results suggest that important welfare gains can be achieved by reducing additive trade costs, not much progress has been done in quantifying such gains. One potential reason is the lack of an empirical characterization of the additive component of trade costs (the one exception being \citet{Irrazabal_2015}). One contribution of the paper is to fill this gap.}

Closely related to our paper is the work by \citet{Irrazabal_2015}, which develop a structural framework for inferring additive trade costs from firm-level trade data. Based on Norwegian firm-level export data in 2004, they find that the ratio of additive to ad-valorem trade costs is about 14\% of the export price. Our results share in common with \citet{Irrazabal_2015} the important role of the additive component of international trade costs. Yet, our paper complements their findings in two main respects. First, while our study covers a narrower set of trade costs focused on transport costs, their data only allows recovering the ratio of additive to ad-valorem costs as a fraction of export price; in contrast, our empirical framework provides a distinct measure of each additive and ad-valorem cost component. From this, we can rebuilt the ratio in similar terms to them, thereby gaining in generality in this respect. Based on the estimated share of transport costs in total trade costs provided by \citet{anderson_wincoop_jel} (around 15\%), straightforward calculation yields a ratio of additive to multiplicative transport (and not trade) costs of 2.1\% (14\% $\times$ 15\%) in \citet{Irrazabal_2015}. This falls in the range of our own estimates, and makes us confident in our quantitative assessment of the size of international transport costs. \footnote{See Section \ref{sec:results_decomposition} for more details.} Second, we exploit exhaustive information about the imports flows of the US over a large time span from 1974 to 2013. In this respect, our results deliver a broader view of the magnitude of additive costs in international trade over time. In particular, we show that the modeling of additive costs is of critical importance in determining the underlying sources of the trends patterns of international transport costs observed since 1974.\footnote{On top of the previously cited papers about additive costs, our paper also relates to \citet{Kropf-Saure-JIE-2016}, which estimate the size and shape of per-shipment costs bases on Swiss data, and to \citet{Alessandria-et-al-AER-2010}, \citet{Hornok-et-al-RES-2015} and \citet{Hornok-et-al-JIE-2015}, which point out the role of per-shipment costs (among which, administrative costs) in generating some ``lumpiness'' in international trade transactions.} \smallskip

@@

Our analysis of transportation costs consists in exploiting the difference between commodity-level export and import prices, as in \cite{hummels2007} (among others). The database we use to construct our measure of transport costs comes from US annual Imports of Merchandise provided by the Census bureau,\footnote{More information available at: \url{http://www.census.gov/foreign-trade/reference/products/catalog/fl_imp.txt}} spanning from 1974 to 2013. We first use customs values, quantities and freight costs to recover free-alongside (fas) and cost-insurance-fret (cif) prices, by goods, country of origin and transportation mode.\footnote{The related literature commonly refers to the fob price rather than the fas price. The fas price (for ``Free Alongside Ship'') means that the seller must transport the goods all the way to the dock, close enough to be reached by the crane of the ship it will be transported in. It is also the seller's responsibility to clear the goods for export. The fob price (for ``Free on Board'') means that the seller is obligated to bring the goods all the way to the port, clear the goods for export, and see that they are loaded onto the ship nominated by the buyer. Once the goods clear the railing of the vessel the buyer assumes the risk. Note that this term is used exclusively for maritime and inland waterway transport. While both terms are closely related, we refer to the fas price as the price considered by the US Foreign Trade Statistics.} More precisely, the (unit) fas price is computed as the total ``customs value'' in the US trade statistics divided by the shipping weight; in other words, it is the price for one kg of the good net of transportation costs. The cif price is then computed as the sum of the customs value and freight charges, once again divided by the shipping weight. Our dependant variable is finally computed as the ratio of the cif price divided by the fas price. Higher than 1, the variable provides a measure of transport costs as a proportion of the good's price, an \emph{ad-valorem} equivalent. This is a quite standard and widespread strategy, as emphasized by \citet{anderson_wincoop_jel}.

@@

We estimate international transport costs at the 3-digit classification level, even if data series on the cif and fas prices are available at the 5-digit classification level. As detailed below, the use of a nonlinear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time. Yet, we ensure the robustness of these results by conducting the estimations at the 4-digit level for some selected years.\footnote{The selected years for the 4-digit level estimations are: 1974, 1977, 1981, 1985, 1989, 1993, 1997, 2001, 2005, 2009, 2013. Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation. However, we obtain no substantial difference between the estimation results conducted at the 3 and 4-digit levels. Estimation results at the 4-digit classification level are reported in Appendix \ref{app:4digit}.} Depending on the considered year, this leaves us with around 200 sectors, from approximately 200 countries of origin.

@@

The Customs value is the value of imports as appraised by the U.S. Customs and Border Protection in accordance with the legal requirements of the Tariff Act of 1930, as amended. This value is generally defined as the price actually paid or payable for merchandise when sold for exportation to the United States, excluding U.S. import duties, freight, insurance, and other charges incurred in bringing the merchandise to the United States. The term ``price actually paid or payable'' means the total payment (whether direct or indirect, and exclusive of any costs, charges, or expenses incurred for transportation, insurance, and related services incident to the international shipment of the merchandise from the country of exportation to the place of importation in the United States) made, or to be made, for imported merchandise by the buyer to, or for the benefit, of the seller. In this respect, the ``custom value'' corresponds to the fas price (``free-alongside'' price) delivered by the seller.

>>>>

\begin{abstract}
This paper investigates the underlying sources behind the downward trend of international transport costs, exploiting information contained in the US imports flows database over 1974-2013 distinguished by transport mode, air and vessel. This drives us to provide a careful modeling of international transport costs, that allows for both ad-valorem (multiplicative) and per-unit (additive) components. In contrast to \cite{hummels2007}, we find that composition effects play a minor role in accounting for the reduction of transport costs relative to the value of US imports. Transport cost ``per se'' did decline. Importantly, this difference of results can be attributed to the new way of modeling the additive component of transport costs we offer. Further, in quantitative terms, we find that the additive component of transport costs is sizeable, representing between 40 and 50\% of overall transport costs. In both aspects, our results point the importance of the additive component in accounting for international transport costs.
\end{abstract}

@@

This focus is shared with part of the international trade literature that studies the patterns of transport costs over time, such as \cite{hummels2007} and \cite{Behar_Venables} (among others). Many argue that transport costs have substantially decreased with technological advance in transportation, infrastructure development and new communication technologies (see \citealp{Lafourcade_Thisse}). %According to \cite{Glaeser04}, over the twentieth century, the cost of moving goods inland have declined by over 90\% in real terms.
The container was a major transport-cost reducing innovation (see \citealp{levinson2016box}). However, \cite{hummels2007} points out that trade composition effects dominate the characterization of time trends of international transport costs and that transport costs ``per se'' (i.e., \textit{ceteris paribus} for given goods, mode, and trade routes) have not declined much. In this paper, we investigate the robustness of this result. As a major contribution, and in contrast to \cite{hummels2007}, we find that trade composition effects play a minor role in accounting for the trend patterns of transport costs. Rather, transport costs ``per se'' did decline, in both transport modes, and this is constitutes the main driving force behind the overall transport costs decrease, in particular for air transport.\medskip

To prove this point we provide a careful modelling of transport costs. Following \citet{samuelson1954}, standard models of international trade have usually modeled trade costs as an \emph{ad-valorem} tax equivalent (ie, as a constant percentage of the producer price per unit traded, part of the ``iceberg cost'' hypothesis).\footnote{Strictly speaking, the ``iceberg cost'' includes both the ad-valorem dimension of trade cost and the fact that these costs are paid in terms of the good that is traded. As this last element is irrelevant in our case, we use the terms ``iceberg'' and ``ad-valorem'' interchangeably, as it is commonly done in the literature.} However, a recent strand of the literature points out to the existence of an additive component, that is, a cost per unit traded (see the references below). Based on US sectoral data, our own estimates also bring out the importance of additive costs in international transport costs. This is obtained by providing an empirical decomposition of the structure of transport costs over time, in which we explicitly distinguish between ad-valorem and additive parts. To do so, we exploit information contained in the US imports flows over 1974-2013, from which we get a measure of international transport costs as the difference between the import and the export prices, on a year-product-partner country basis. This database is the same as \cite{hummels2007}, extended over the more recent years (2005-2013). \smallskip

Our results may be summarized in two main new findings. First, additive transport costs are quantitatively sizeable. On average over 1974-2013, the additive cost is estimated to be 1.8\% and 2.9\% of the export price in air and vessel transport respectively. This is slightly lower than our estimates for the ad-valorem component (3.5\% and 3.2\% for air/vessel respectively on average over the period). Put it differently, additive costs represent between 40 \% and 50\% of the overall transport costs, depending on the year and the transport mode. To the best of our knowledge, our paper is the first to provide such an extensive quantitative measure of both ad-valorem and additive costs in total transport costs. This represents a valuable insight for calibrating related international trade or business cycle models. We also provide an empirical assessment of what standard international trade models lose by skipping additive transport costs. Quantitatively, the omission of the additive term leads to overestimate the ad-valorem component by roughly a factor~2. Additionally, the goodness of fit is systematically better when the additive component is included in the regression, even when taking into account the additional degrees of freedom. \textbf{attention maintenant en annexe. Le dire en intro, est ce pertinent?}

Second, we find that the main source of the downward trend in overall transport costs (that decreased by roughly 50\% in air shipping and 60\% in vessel shipping over 1974-2013) does come from the reduction of transport cost ``per se'', rather than from trade composition effects. This stands in sharp contrast to the conclusion obtained by \cite{hummels2007} on the same database (until 2004). Importantly, we show that the difference of results can be attributed to the new way of modeling of the additive component we offer. Allowing the additive costs to vary  across time, products and country partners (rather than being constant as in \citealp{hummels2007}), turns out to be key in the decomposition of underlying sources of the decrease of overall transport costs observed over the period. Our result is more in line with common knowledge observations of the reduction of transport costs due, e.g., to the diffusion of the container.\smallskip

In both aspects, our results point the importance of the additive component in accounting for international transport costs. In this respect, it contributes to the literature that challenges the dominant role of iceberg costs in international trade (even in the case of ice transport: see \citealp{bosker2018ice}). As underlined by \cite{alchian}, the relative price of two varieties of some good will depend on the level of trade costs as long as they display an additive component. In this context, the relative demand for more expensive/higher quality product goods increases with trade costs (``shipping the good apples out''). This is consistent with the findings by \citet{hummels_skiba}, who estimate the elasticity of freight rates with respect to price to be well below unity. Also, their estimates imply that doubling freight costs increases average free alongside (fas) export prices by 80 to 141 percent, consistent with high quality goods being sold in markets with high freight costs. \citet{Lashkaripour-mimeo-2017} challenges this view. Highlighting that more expensive goods are systematically heavier (and hence more costly to transport\footnote{Yet, one can be concerned by the generality of this result. While the positive correlation between weight and price seems reasonable for goods from the second industrial revolution like cars, it is dubious in the case of ITC goods whose importance in international trade has been rising since the end of the twentieth century.}), he finds an average transport cost elasticity much closer to 1 using firm-level data on Colombian imports. This result is also confirmed on more aggregate US, sector-level trade data. The debate is not over yet, as recent empirical studies based on micro-level data conversely provide a strong empirical support to the role of additive costs (i.e., cost per unit exported) in international trade costs. Based on a firm-product-level database of French exporters, \citet{martin2012} finds that firms charge higher unit values for exports to more remote countries, in contradiction with the ad-valorem hypothesis.\footnote{Beyond the positive aspect, several recent papers also point out the normative implications of additive trade costs. \citet{sorensen2014} extends \citet{melitz}'s seminal model of international trade by including additive trade costs, in addition to the ad-valorem component. A key analytical result is that the welfare gain from a reduction in trade barriers is higher for a decrease in additive costs than a decrease in ad-valorem costs, due to the alteration of relative prices in a heterogeneous-firms trade framework. This is confirmed by \cite{Irrazabal_2015}. While these results suggest that important welfare gains can be achieved by reducing additive trade costs, not much progress has been done in quantifying such gains. One potential reason is the lack of an empirical characterization of the additive component of trade costs (the one exception being \citet{Irrazabal_2015}). One contribution of the paper is to fill this gap.}

Closely related to our paper is the work by \citet{Irrazabal_2015}, which develop a structural framework for inferring additive trade costs from firm-level trade data. Based on Norwegian firm-level export data in 2004, they find that the ratio of additive to ad-valorem trade costs is about 14\% of the export price. Our results share in common with \citet{Irrazabal_2015} the important role of the additive component of international trade costs. Yet, our paper complements their findings in two main respects. First, while our study covers a narrower set of trade costs focused on transport costs, their data only allows recovering the ratio of additive to ad-valorem costs as a fraction of export price; in contrast, our empirical framework provides a distinct measure of each additive and ad-valorem cost component. From this, we can rebuilt the ratio in similar terms to them, thereby gaining in generality in this respect. Based on the estimated share of transport costs in total trade costs provided by \citet{anderson_wincoop_jel} (around 15\%), straightforward calculation yields a ratio of additive to multiplicative transport (not trade) costs of 2.1\% (14\% $\times$ 15\%) in \citet{Irrazabal_2015}. This falls in the range of our own estimates, making us confident in our quantitative assessment of the size of international transport costs. \footnote{See Section \ref{sec:results_decomposition} for more details.} Second, we exploit exhaustive information about the imports flows of the US over a large time span from 1974 to 2013. In this respect, our results deliver a broader view of the magnitude of additive costs in international trade over time. In particular, we show that the modeling of additive costs is of critical importance in determining the underlying sources of the trends patterns of international transport costs observed since 1974.\footnote{On top of the previously cited papers about additive costs, our paper also relates to \citet{Kropf-Saure-JIE-2016}, which estimate the size and shape of per-shipment costs bases on Swiss data, and to \citet{Alessandria-et-al-AER-2010}, \citet{Hornok-et-al-RES-2015} and \citet{Hornok-et-al-JIE-2015}, which point out the role of per-shipment costs (among which, administrative costs) in generating some ``lumpiness'' in international trade transactions.} \smallskip

\textbf{enleve ancienne footnote plus haut qui reprenait cette difference, a mettre en footnote ici? en commentaire en dessous}
%\footnote{As we discuss below, the closest paper to us in this respect is \citet{Irrazabal_2015}. However, given their database and their empirical approach, \citet{Irrazabal_2015} can only identify the ratio of the additive to the ad-valorem cost ($\frac{t_{ik}}{\tau_{ik}}$ in our terminology), that they interpret by expressing it in terms of the median export price by country-product ($\bar{\widetilde{p}}_{ik}$). By contrast, our estimation strategy enables us to uncover both values of the ad-valorem and the additive costs $\tau_{ik}$ and $t_{ik}$ separately, in terms of the country-product export price $\widetilde{p}_{ik}$.}

@@

Our analysis of transportation costs consists in exploiting the difference between commodity-level export and import prices, as in \cite{hummels2007} (among others). The database we use to construct our measure of transport costs comes from US annual Imports of Merchandise provided by the Census bureau, spanning from 1974 to 2013. Details on the database are provided in Appendix \ref{app:data}. We first use customs values, quantities and freight costs to recover free-alongside (fas) and cost-insurance-fret (cif) prices, by goods, country of origin and transportation mode.\footnote{The related literature commonly refers to the fob price rather than the fas price. The fas price (for ``Free Alongside Ship'') means that the seller must transport the goods all the way to the dock, close enough to be reached by the crane of the ship it will be transported in. It is also the seller's responsibility to clear the goods for export. The fob price (for ``Free on Board'') means that the seller is obligated to bring the goods all the way to the port, clear the goods for export, and see that they are loaded onto the ship nominated by the buyer. Once the goods clear the railing of the vessel the buyer assumes the risk. Note that this term is used exclusively for maritime and inland waterway transport. While both terms are closely related, we refer to the fas price as the price considered by the US Foreign Trade Statistics.} More precisely, the (unit) fas price is computed as the total ``customs value'' in the US trade statistics divided by the shipping weight; in other words, it is the price for one kg of the good net of transportation costs. The cif price is then computed as the sum of the customs value and freight charges, once again divided by the shipping weight. Our dependant variable is finally computed as the ratio of the cif price divided by the fas price. Higher than 1, the variable provides a measure of transport costs as a proportion of the good's price, an \emph{ad-valorem} equivalent. This is a quite standard and widespread strategy, as emphasized by \citet{anderson_wincoop_jel}.

@@

We estimate international transport costs at the 3-digit classification level, even if data series on the cif and fas prices are available at the 5-digit classification level. As detailed below, the use of a nonlinear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time. Yet, we ensure the robustness of these results by conducting the estimations at the 4-digit level for some selected years.\footnote{The selected years for the 4-digit level estimations are: 1974, 1977, 1981, 1985, 1989, 1993, 1997, 2001, 2005, 2009, 2013. Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation. However, we obtain no substantial difference between the estimation results conducted at the 3 and 4-digit levels. Estimation results at the 4-digit classification level are reported in Appendix \ref{app:4digit}.} Depending on the considered year, this leaves us with around 200 sectors at the 3-digit level, from approximately 200 countries of origin.

\textbf{stop here}

@@

The Customs value is the value of imports as appraised by the U.S. Customs and Border Protection in accordance with the legal requirements of the Tariff Act of 1930, as amended. This value is generally defined as the price actually paid or payable for merchandise when sold for exportation to the United States, excluding U.S. import duties, freight, insurance, and other charges incurred in bringing the merchandise to the United States. The term ``price actually paid or payable'' means the total payment (whether direct or indirect, and exclusive of any costs, charges, or expenses incurred for transportation, insurance, and related services incident to the international shipment of the merchandise from the country of exportation to the place of importation in the United States) made, or to be made, for imported merchandise by the buyer to, or for the benefit, of the seller. In this respect, the ``custom value'' corresponds to the fas price (``free-alongside'' price) delivered by the seller. More information on this database is available at: \url{http://www.census.gov/foreign-trade/reference/products/catalog/fl_imp.txt}.
